A Seamless, Client-Centric Programming Model for Type Safe Web Applications

### 2014-06-25 haskell10f-ekblad.tex
Some formatting fixes + copyright info for publishing.
Add acknowledgement for RAWFP funding.
Fix bug in JS example.

\documentclass[preprint]{sigplanconf}

@@

\conferenceinfo{ICFP~'14}{September 1--3, 2014, Gothenburg, Sweden} 
\copyrightyear{2014}
\copyrightdata{978-1-nnnn-nnnn-n/14/09}
\doi{nnnnnnn.nnnnnnn}

@@

%\exclusivelicense                % ACM gets exclusive license to publish, 
                                  % you retain copyright

@@

\title{A seamless, client-centric programming model for type safe web applications}

@@

  sock.onopen = function(e) {
    handshake(sock);
    msgbox.addEventListener('keydown', function(e) {
      if(e.keyCode == 13) {
        var msg = msgbox.value;
        msgbox.value = '';
        chat(msg);
      }
    });
  };
};
\end{lstlisting}
\caption{JavaScript chatbox implementation}
\label{lst:javascript-client}
\end{listingfloat}

@@

>>>>

\documentclass{sigplanconf}

@@

\exclusivelicense
\conferenceinfo{ICFP~'14}{September 6, 2014, Gothenburg, Sweden}
\copyrightyear{2014}
\copyrightdata{978-1-4503-3041-1/14/09}
\doi{2633357.2633367}

@@

@@

\title{A Seamless, Client-Centric Programming Model for Type Safe Web Applications}

@@

  sock.onopen = function(e) {
    handshake(sock);
    msgbox.addEventListener('keydown', function(e) {
      if(e.keyCode == 13) {
        var msg = msgbox.value;
        msgbox.value = '';
        chat(sock, msg);
      }
    });
  };
};
\end{lstlisting}
\caption{JavaScript chatbox implementation}
\label{lst:javascript-client}
\end{listingfloat}

@@

\acks
This work has been partially funded by the Swedish Foundation for Strategic Research, under grant RAWFP.
